% Timothy Chumley - Curriculum Vitae
% tchumley@gmail.com


\documentclass[10pt,letterpaper]{article}

\usepackage{hyperref}
\usepackage{geometry}
\usepackage{enumitem}
\usepackage{etoolbox}


% Fonts
\usepackage[T1]{fontenc}
%\usepackage[urw-garamond]{mathdesign}

% Set your name here
\def\name{Timothy Chumley}

% The following metadata will show up in the PDF properties
\hypersetup{
  colorlinks = true,
  urlcolor = black,
  pdfauthor = {\name},
  pdfkeywords = {mathematics, probability, dynamical systems, billiards},
  pdftitle = {\name: Curriculum Vitae},
  pdfsubject = {Curriculum Vitae},
  pdfpagemode = UseNone
}

\geometry{
  body={6.5in, 9.0in},
  left=1.0in,
  top=1.0in
}

% Customize page headers
\pagestyle{myheadings}
\markright{\name}
\thispagestyle{empty}

% Custom section fonts
\usepackage{sectsty}
\sectionfont{\rmfamily\mdseries\Large}
\subsectionfont{\rmfamily\mdseries\itshape\large}

% Other possible font commands include:
% \ttfamily for teletype,
% \sffamily for sans serif,
% \bfseries for bold,
% \scshape for small caps,
% \normalsize, \large, \Large, \LARGE sizes.

% Don't indent paragraphs.
\setlength\parindent{0em}

% Make lists without bullets and compact spacing
\renewenvironment{itemize}{
  \begin{list}{}{
    \setlength{\leftmargin}{1.5em}
    \setlength{\itemsep}{0.25em}
    \setlength{\parskip}{0pt}
    \setlength{\parsep}{0.25em}
  }
}{
  \end{list}
}
\setlist[enumerate]{itemsep=0.25em}

\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\let\tightlist\relax

% Toggles
% set 'long' to TRUE for long CV version
% set 'teaching' to TRUE for teaching oriented CV
\newtoggle{long}
\toggletrue{long}
\newtoggle{teaching}
%\toggletrue{teaching}

\begin{document}

% Place name at left
{\huge \name}

% Alternatively, print name centered and bold:
%\centerline{\huge \bf \name}

\bigskip

\begin{minipage}[t]{0.495\textwidth}
  Department of Mathematics \& Statistics \\
  Mount Holyoke College \\
  50 College St \\
  South Hadley, MA 01075
\end{minipage}
\begin{minipage}[t]{0.495\textwidth}
  Phone: (413) 538-2525 \\
  Office: 423 Clapp Lab \\
  Email: \href{mailto:tchumley@mtholyoke.edu}{\tt tchumley@mtholyoke.edu} \\
  Homepage: \url{http://tchumley.mtholyoke.edu}
\end{minipage}

\hypertarget{education}{%
\section*{Education}\label{education}}
\addcontentsline{toc}{section}{Education}

\begin{itemize}
\tightlist
\item
  Washington University in St.~Louis, Ph.D.~in Mathematics, 2013
\item
  Marquette University, M.S. in Mathematics, 2007
\item
  Marquette University, B.S. in Computer Science, Mathematics, 2005
\end{itemize}

\hypertarget{employment}{%
\section*{Employment}\label{employment}}
\addcontentsline{toc}{section}{Employment}

\begin{itemize}
\tightlist
\item
  Mount Holyoke College, Department of Mathematics \& Statistics

  \begin{itemize}
  \tightlist
  \item
    Assistant Professor, 2016 -- 2022
  \item
    Associate Professor, 2022 -- present
  \end{itemize}
\item
  Iowa State University, Department of Mathematics

  \begin{itemize}
  \tightlist
  \item
    NSF Alliance for Building Faculty Diversity Postdoctoral Fellow,
    2013 -- 2016
  \end{itemize}
\item
  Washington University in St.~Louis, Department of Mathematics

  \begin{itemize}
  \tightlist
  \item
    Graduate Teaching Assistant and Instructor, 2008 -- 2013
  \end{itemize}
\end{itemize}

\hypertarget{teaching}{%
\section*{Teaching}\label{teaching}}
\addcontentsline{toc}{section}{Teaching}

\hypertarget{mount-holyoke-college}{%
\subsection*{Mount Holyoke College}\label{mount-holyoke-college}}
\addcontentsline{toc}{subsection}{Mount Holyoke College}

\begin{itemize}
\item
  Math 241, Dynamical Systems, Spring 2022.
\item
  Math 339SP/Stat 344, Stochastic Processes, Spring 2022.
\item
  Math 102, Calculus II, Fall 2021.
\item
  Math 301, Real Analysis, Fall 2021.
\item
  Math 342, Probability (2 sections), Spring 2021.
\item
  Math 395, Independent study in Billiards and Thermodynamics (1
  student), Spring 2021.
\item
  Math 301, Real Analysis (2 sections), Fall 2020.
\item
  Math 101, Calculus I, Spring 2019.
\item
  Math 339SP/Stat 344, Stochastic Processes, Spring 2019.
\item
  Math 395, Independent study in Random Billiards (1 student), Spring
  2019.
\item
  Math 232, Discrete Math, Fall 2018.
\item
  Math 342, Probability, Fall 2018.
\item
  Math 395, Independent study in Random Billiards (1 student), Fall
  2018.
\item
  Math 339SP/Stat 344, Stochastic Processes, Spring 2018.
\item
  Math 333, Differential Equations, Spring 2018.
\item
  Math 342, Probability (2 sections), Fall 2017.
\item
  Stat 395, Independent study in Statistical Analysis of Networks (3
  students), Fall 2017.
\item
  Student Research (2 students), Summer 2017.
\item
  Math 211, Linear Algebra, Spring 2017.
\item
  Math 339SP/Stat 344, Stochastic Processes, Spring 2017.
\item
  Math 102, Calculus II, Fall 2016.
\item
  Math 342, Probability, Fall 2016.
\end{itemize}

\hypertarget{iowa-state-university}{%
\subsection*{Iowa State University}\label{iowa-state-university}}
\addcontentsline{toc}{subsection}{Iowa State University}

\begin{itemize}
\item
  Math 166, Calculus II, Fall 2015.
\item
  Math 501, Introduction to Real Analysis, Fall 2014.
\item
  Math 317, Theory of Linear Algebra, Spring 2014.
\item
  Math 166, Calculus II, Fall 2013.
\end{itemize}

\hypertarget{washington-university}{%
\subsection*{Washington University}\label{washington-university}}
\addcontentsline{toc}{subsection}{Washington University}

\begin{itemize}
\item
  Math 309, Matrix Algebra, Summer 2012.
\item
  Math 1011, Introduction to Statistics, Summer 2010.
\item
  Math 1011, Introduction to Statistics, Summer 2009.
\item
  Math 155, Calculus I, Summer 2008.
\end{itemize}

\hypertarget{research-articles}{%
\section*{Research Articles}\label{research-articles}}
\addcontentsline{toc}{section}{Research Articles}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  \protect\hypertarget{CFG2020}{}{} T.~Chumley, R.~Feres, and L.~A.
  Garcia German. Knudsen diffusivity in random billiards: spectrum,
  geometry, and computation. \emph{SIAM J. Appl. Dyn. Syst.},
  20(3):1655--1682, 2021.
\item
  \protect\hypertarget{CFW2016}{}{} T.~Chumley, R.~Feres, and
  M.~Wallace. Exact discretization of harmonic tensors. \emph{Potential
  Anal.}, 56(3):409--421, 2022.
\item
  \protect\hypertarget{CF2019}{}{} T.~Chumley and R.~Feres. Entropy
  production in random billiards. \emph{Discrete Contin. Dyn. Syst.},
  41(3):1319--1346, 2021.
\item
  \protect\hypertarget{CCCF2018}{}{} T.~Chumley, S.~Cook, C.~Cox, and
  R.~Feres. Rolling and no-slip bouncing in cylinders. \emph{J. Geom.
  Mech.}, 12(1):53--84, 2020.
\item
  \protect\hypertarget{ACMR2016}{}{} O.~Aydogmus, T.~Chumley,
  A.~Matzavinos, and A.~Roitershtein. Moran-type bounds for the fixation
  probability in a frequency-dependent Wright-Fisher model. \emph{J.
  Math. Biol.}, 76(1):1--35, 2018.
\item
  \protect\hypertarget{CFZ2016}{}{} T.~Chumley, R.~Feres, and H.-K.
  Zhang. Diffusivity in multiple scattering systems. \emph{Trans. Amer.
  Math. Soc.}, 368(1):109--148, 2016.
\item
  \protect\hypertarget{CCF2013}{}{} T.~Chumley, S.~Cook, and R.~Feres.
  From billiards to thermodynamics. \emph{Comput. Math. Appl.},
  65(10):1596--1613, 2013.
\item
  \protect\hypertarget{CT}{}{} T.~Chumley. \emph{Limit Theorems for
  Random Billiard Models}. PhD thesis, 2013.
\end{enumerate}

\hypertarget{invited-presentations}{%
\section*{Presentations}\label{invited-presentations}}
\addcontentsline{toc}{section}{Presentations}

\hypertarget{invited}{%
\subsubsection*{Invited}\label{invited}}
\addcontentsline{toc}{subsubsection}{Invited}

\begin{itemize}
\item
  Tarleton State University, Colloquium, September 2019
\item
  SIAM Conference on Applications of Dynamical systems, Minisymposium on
  Thermodynamic Laws from Nonequilibrium Dynamics, May 2019
\item
  AMS Eastern Sectional Meeting, Special Session on Billiard Dynamics:
  Standard and Alternative Collision Models, September 2018
\item
  Joint Mathematics Meetings, Special session on Research by Postdocs of
  the Alliance for Diversity in Mathematics, January 2018
\item
  AIMS Conference on Dynamical Systems, Differential Equations and
  Applications, Special Session on Dynamical systems and their
  applications, July 2016
\item
  Washington University, Geometry seminar, April 2016
\item
  Mount Holyoke College, Colloquium, February 2016
\item
  Joint Mathematics Meetings, Special session on Research by Postdocs of
  the Alliance for Diversity in Mathematics, January 2016
\end{itemize}

\hypertarget{contributed}{%
\subsubsection*{Contributed}\label{contributed}}
\addcontentsline{toc}{subsubsection}{Contributed}

\begin{itemize}
\item
  International Congress of Mathematicians, Probability session, August
  2018
\item
  Seminar on Stochastic Processes, University of Virginia, March 2017
\end{itemize}

\hypertarget{professional-service}{%
\section*{Professional Service}\label{professional-service}}
\addcontentsline{toc}{section}{Professional Service}

\begin{itemize}
\tightlist
\item
  Co-organizer for Special Session at AMS Fall Eastern Sectional
  Meeting, October 2022
\item
  Panelist for Applied Math program, Division of Mathematical Sciences,
  NSF, March 2022
\item
  Co-organizer, BIRS Oaxaca workshop on Frontiers in Billiard Dynamics,
  June 2021
\item
  Co-organizer, SIAM Conference on Applications of Dynamical systems
  mini-symposium, May 2019
\item
  Co-organizer for Special Session at AMS Fall Eastern Sectional
  Meeting, September 2018
\item
  Judge for MAA Undergraduate Poster Session at JMM, January 2017
\item
  Co-organizer for Special Session at 11th AIMS Conference on Dynamical
  Systems Differential Equations and Applications, Orlando, July 2016
\item
  Co-organizer for AIM SQuaRE on Stochastic thermodynamics and random
  billiards, 2015 -- 2017
\item
  Co-organizer, Iowa State University probability seminar, 2014 -- 2016
\item
  Co-organizer for AMS Special session on Statistical Aspects of
  Dynamical Systems, October 2013
\item
  Referee for Chaos: An Interdisciplinary Journal of Nonlinear Science,
  Discrete and Continuous Dynamical Systems, Journal of Mathematical
  Physics
\end{itemize}

\hypertarget{awards-grants-and-other-honors}{%
\section*{Awards, Grants, and Other
Honors}\label{awards-grants-and-other-honors}}
\addcontentsline{toc}{section}{Awards, Grants, and Other Honors}

\begin{itemize}
\tightlist
\item
  Interviewed for AMS Mathematical Moments, 2022.
\item
  Featured in Latinxs and Hispanics in the Mathematical Sciences AMS
  poster, 2022
\item
  Featured in MAA Focus article on Latinxs and Hispanics in the
  Mathematical Sciences, 2020.
\item
  Latinxs and Hispanics in the Mathematical Sciences (Lathisms) honoree,
  2020
\item
  AMS-NSF International Congress of Mathematicians travel award, 2014,
  2018, 2022
\item
  AMS Project NExT Fellow, 2016 -- 2017
\item
  American Institute of Mathematics SQuaRE grant, 2015 -- 2017
\item
  NSF Alliance for Diversity in Mathematical Sciences Postdoctoral
  Fellowship, 2013 -- 2016
\item
  Dissertation Fellowship, Washington University, 2012 -- 2013
\item
  University Fellowship, Washington University, 2007 -- 2008, 2010
\item
  Phi Beta Kappa, 2005
\end{itemize}

\hypertarget{selected-conference-participation}{%
\section*{Selected Conference
Participation}\label{selected-conference-participation}}
\addcontentsline{toc}{section}{Selected Conference Participation}

\begin{itemize}
\item
  Northeast Conference on Dynamical Systems, University of Massachusetts
  Amherst, November 2019.
\item
  Illustrating Probability and Dynamics workshop, ICERM, November 2019.
\item
  SIAM Conference on Applications of Dynamical systems, Snowbird, May
  2019.
\item
  AMS Eastern Sectional Meeting, Newark, September 2018.
\item
  International Congress of Mathematicians, Rio de Janeiro, August 2018.
\item
  Seminar on Stochastic Processes, Brown University, May 2018.
\item
  Joint Mathematics Meetings, San Diego, January 2018.
\item
  Mathfest, Chicago, August 2017.
\item
  AIM SQuaRE on Stochastic thermodynamics and random billiards, June
  2017
\item
  Seminar on Stochastic Processes, University of Virginia, March 2017.
\item
  Joint Mathematics Meetings, Atlanta, January 2017.
\item
  Mathfest, Columbus, August 2016.
\item
  The 11th AIMS Conference on Dynamical Systems, Differential Equations
  and Applications, Orlando, July 2016.
\end{itemize}

\hypertarget{service-at-mount-holyoke-college}{%
\section*{Service at Mount Holyoke
College}\label{service-at-mount-holyoke-college}}
\addcontentsline{toc}{section}{Service at Mount Holyoke College}

\begin{itemize}
\tightlist
\item
  Academic Administrative Board member, 2020 -- 2023
\item
  Math/Stat liaison for STEMPOC student group, 2018 -- 2020
\item
  Subcommittee on the Goldwater Fellowship, 2017 -- 2020
\item
  Math/Stat TAs and graders co-organizer, 2017 -- 2018
\item
  Data science curriculum committee, 2016 -- 2017
\item
  Problem solving club co-advisor, 2016 -- 2017
\item
  Math/Stat LITS liaison, 2016 -- 2017
\end{itemize}

\hypertarget{professional-memberships}{%
\section*{Professional Memberships}\label{professional-memberships}}
\addcontentsline{toc}{section}{Professional Memberships}

\begin{itemize}
\tightlist
\item
  Member, American Mathematical Society, 2007 -- Present.
\item
  Member, Mathematical Association of America, 2016 -- Present.
\end{itemize}
% Footer
\bigskip
{\small Last updated: \today}

\end{document}
